\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{charter}
\usepackage{xcolor}
\usepackage{array}
\usepackage{url}

% - Dimensions -
\voffset=0.0in
\topmargin=0.0in
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=450pt
\textheight=800pt
\headheight=0.0in
\headsep=0.0in
\footskip=0.0in

% - Bookkeeping -
\pagenumbering{gobble}
\pagestyle{empty}

% - Customization -
\setlength{\parindent}{0pt}

% - Commands -
\definecolor{lgray}{gray}{1.0}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand{\VRule}{\color{lgray}\vrule width 0.5pt}

\newenvironment{cvcol}%
{\begin{tabular}{L!{\VRule}R}}%
{\end{tabular}}

\newcommand{\cvsec}[2][]{{\bf #1}&{\bf #2}\smallskip\\}
\newcommand{\cvpar}[2][]{{\bf #1}&#2\\}
\newcommand{\cvskip}{&\\}

% - Curriculum Vitae -
\begin{document}

% - Title -
\centerline{\LARGE\bf Siddharth Mahendraker}
\medskip

% - Personal Info -
\centerline{Mäenrinne 3-5 K 90, Espoo, Finland}
\smallskip
\centerline{+358 40 142 2010}
\smallskip
\centerline{\href{mailto:siddharth_mahen@me.com}{\url{siddharth_mahen@me.com}}}
\rule{\textwidth}{0.2pt}

\section*{Objective}
I'm a young, focused and talented student looking for a challenging job
oppertunity where I can apply my knowledge of mathematics and computer
science.

\section*{Education}
\begin{cvcol}
\cvsec[2010 -- now]{International School of Helsinki, Helsinki, Finland, Grades 9 - 11}
\cvpar{Currently in the 11th grade. Graduated each previous year with honours.}
\cvskip
\cvsec[2006 -- 2010]{West Oak Public School, Oakville, Ontario, Canada, Grades 5 - 8}
\cvpar{Graduated each year with honours. Valedictorian of the graduating class.
Received the French award for excellence in the French language.}
\end{cvcol}

\section*{Work Experience}
\begin{cvcol}
\cvsec[2010 -- 2011]{Engineered an iPhone application used in production at iMenu360 Inc.}
\cvpar{Was responsible for planning, designing, engineering and coding the
application on behalf of iMenu360. The application displayed incoming orders
for restaurant managers, allowing them to quickly understand an order
issue and take corrective action. The application incorporated push
notifications, XML parsing and custom gestures.}
\end{cvcol}

\section*{Interests}
\begin{cvcol}
\cvpar[Mathematics]{
Particularly number theory, abstract algebra and cryptography. In the
10\textsuperscript{th} grade, wrote a through report on modern cryptography,
with an emphasis on the mathematical cryptanalysis of these techniques (available
at \url{http://git.io/iAFH6A}).}
\cvskip
\cvpar[Theoretical and Applied Computer Science]{
Particularly the design and analysis of algorithms and data structures, and
the theory of computation. Pioneered the computer science course at the
International School of Helsinki.}
\cvskip
\cvpar[Open Source Software]{
Regularly work on small open source projects in leisure time. Maintainer
of two non-trivial open source projects. Has contributed minor patches to
larger projects such as the node.js project. All code freely available under the
MIT licence at \url{https://github.com/siddmahen}.}
\cvskip
\cvpar[Music]%
{Played 1\textsuperscript{st} flute in the West Oak School Band for 3 years.
Invited to play in the Halton Intermediate Woodwinds Band by recommendation from the
band conductor. Continued to play flute in Helsinki, playing the solo flute score
for the school production of {\it The Wizard of Oz} in 2011.}
\end{cvcol}

\section*{Achievements}
\begin{cvcol}
\cvpar[Student Government]%
{Elected vice-president of the High School Student Council. Have served on
the Council in various capacities for the past 3 years. In charge of planning,
organizing and running large school events such as school dances, cultural and
seasonal events and fund raisers.}
\cvskip
\cvpar[Volleyball]%
{Won Bronze at the CEESA High School Boys Volleyball Tournament, 2012,
Helsinki, Finland. Played as the team setter. Have been playing volleyball for
over 4 years, competitively for the past 2 years.}
\cvskip
\cvpar[Model United Nations]%
{Participated in 5 MUN conferences, including conferences in the
Hague, Paris and Milan. Held various high profile positions; head ambassador
of high profile countries such as Turkey and Japan, member of the Security
Council, the Disarmament Committee and the International Court of Justice.
Recognized at the Milan MUN for outstanding work in the Security Council.
Spoke in front of the General Assembly at every conference.}
\end{cvcol}

\section*{Skills}
\begin{cvcol}
\cvpar[Languages]{Mother tongue English. Nearly native French.}
\cvskip
\cvpar[Programming Languages]{Fluent in Javascript and Objective-C. Can also
write in C, Python, PHP and C++. Mild exposure to Haskell.}
\cvskip
\cvpar[Computer Skills]{Highly proficient in a wide variety of tools, including
the shell, git, vim and Xcode. This document was written in vim using {\large \LaTeX}.}
\end{cvcol}

\end{document}

